---
title: "Alcohol vs Seat choice"
author: "Gil Felix"
date: "Sumemer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor)) 
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

library(ggplot2)

```{r}
library(ggplot2)

# Create the notched box plot with outliers colored red and centered title
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Alcohol Explained by Seat") +
  theme(plot.title = element_text(hjust = 0.5))


```




## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The people in the back are drinking a lot more than the people in the middle and the front. The data shows that min all equals 0, with the median the people in the back have 4 and the people in the middle have 1, the people in front have nothing. There is a big difference between the means, with the back people having the highest of almost a 10 rounded up, the people in the middle have 3, and the the people in the front have a 2 rounded up.

Most people are sitting in the middle, there is 83 of them. The rest are evened out between the back and the front.
## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1))
```

There is a difference between the rows. The back row 

```{r}
# Load required package
library(stats)

# Perform ANOVA
result <- aov(alcohol ~ Seat, data = davisdata)

# Check ANOVA summary
summary(result)


```

```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(result)

# View the results
print(tukey_result)

```


## Conclusions


